\documentclass[12pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\title{INFO263 - Group O}
\author{Gavin McGill, Kirill Kirillov, Luke Woollett.}
\begin{document}
	\maketitle
	
	\paragraph{How the website works. \newline}
	First, we load the index file. This will display a webpage with an map and combobox, centered on Auckland. This combo box is used to select what route you would like to see on the map. This combobox is populated by a database, that has a list of all the routes that auckland metro services. Once you click a option out of the combobox, it will then query the auckland metro API for data about that route, then display it on the map. You can then click on a bus on the map to see detailed information about it. \par
	
	
	Teamwork was odd, as the distribution of teamwork did not work well, since one person could comfortably work on the frontend, and one could work on the backend. This left one person in the lurch, as they could not work on things while others were working on them. 
	
	
	\par To communicate, we used Facebook Messenger. This was good and easy to use, as we already all had it installed on our phones. The original plan was to use slack, but it was abandoned in favour of messenger. 
	
	
	\par To manage and share code, we used a GitHub repository. Kirill set this up, and every time one of us made a significant enough edit to the code, they would push what they had done to the repo. This was good, as we could then rollback code if something went wrong. A problem that we had with this was that one of our group kept commiting all of the edited code that he had done, leading to merge errors and log files being uploaded. 
	
	\paragraph{Seperation of tasks. \newline} 
	Kirill did all the backend interaction with API and database, as well as the JS powering the front end. Gavin did all of the CSS as well as some of the map functionality. Luke wrote the base of the report which Kirill will probably change. 
	
	What went well and what didnt.
	
	
	What we would do differently next time.
	
\end{document}